Plots_OceanProtein

### 2024-06-09 Code/Plots_OceanProtein.Rmd
Generated .tiff

   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))

>>>>

   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig7.tiff")))
